Balance responses in MS

### 2020-02-04 R/msBalance.Rmd
added code to plot normalized EMG

# to calculate normalization coefficients, average across like trials for each patient, limit to a particular normalization window, and calculate maximum values
taRMax = taRAv %>% filter(Time %between% c(0.0, 1.0)) %>% group_by(Group, Participant, `Perturbation Direction`) %>% summarize(Vm = max(V, na.rm = TRUE)) %>% ungroup()
```

@@

```{r normedEMG, out.width = "75%", fig.align = "left", fig.cap = captionNormedEmg}
p = ggplot(taR, aes(x = Time, y = V)) +
  geom_line(color = "Gray90", show.legend = FALSE, alpha = 0.5) +
  geom_line(aes(color = Participant), taRAv, show.legend = FALSE, alpha = 0.5) +
  facet_grid(Group ~ `Perturbation Direction`) +
  theme_minimal_grid() +
  geom_text(mapping = aes(x = 0, y = Vm, color = Participant, label = Participant), data = taRMax %>% group_by(Group, `Perturbation Direction`) %>% top_n(3), show.legend = FALSE)
p
```

>>>>

# to calculate normalization coefficients, average across like trials for each patient, limit to a particular normalization window, and calculate maximum values
taRMax = taRAv %>% filter(Time %between% c(0.0, 1.0)) %>% group_by(Group, Participant, `Perturbation Direction`) %>% summarize(Vm = max(V, na.rm = TRUE)) %>% ungroup()

# take the maximum observed in either the forward or backward directions.
taRMaxMax = taRMax %>% group_by(Participant) %>% summarize(Vm = max(Vm))

# append normed EMG to existing EMG
taR %<>% left_join(taRMaxMax, by = "Participant") %>% mutate(Vn = V / Vm)
taRAv %<>% left_join(taRMaxMax, by = "Participant") %>% mutate(Vn = V / Vm)
```

@@

```{r normedEMG, out.width = "75%", fig.align = "left", fig.cap = captionNormedEmg}
p = ggplot(taR, aes(x = Time, y = Vn)) +
  geom_line(color = "Gray90", show.legend = FALSE, alpha = 0.5) +
  geom_line(aes(color = Participant), taRAv, show.legend = FALSE, alpha = 0.5) +
  facet_grid(Group ~ `Perturbation Direction`) +
  theme_minimal_grid() +
  coord_cartesian(ylim = c(0,2))
p
```
